### 2020-07-29 README.Rmd

```{r}
register("http://cdiac.ornl.gov/ftp/trends/co2/vostok.icecore.co2")
```

@@

```{r}
co2 <- read.table("http://cdiac.ornl.gov/ftp/trends/co2/vostok.icecore.co2", 
                  col.names = c("depth", "age_ice", "age_air", "co2"), skip = 21)
```

>>>>

```{r}
register("https://knb.ecoinformatics.org/knb/d1/mn/v2/object/ess-dive-457358fdc81d3a5-20180726T203952542")
```

@@

```{r}
co2 <- read.table("https://knb.ecoinformatics.org/knb/d1/mn/v2/object/ess-dive-457358fdc81d3a5-20180726T203952542", 
                  col.names = c("depth", "age_ice", "age_air", "co2"), skip = 21)
```
